\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-04-05 paper/manuscript.tex
changed title and abstract

%============Article Title, Authors==================
\title{\vspace{-2cm} Content of Municipal Government Websites }

@@

\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply the expressed agenda model (Grimmer 2010) to this corpus. This topic model allows us to identify which kinds of documents are prone to being modified, added and removed after transitions of power.

>>>>

%============Article Title, Authors==================
\title{\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites }

@@

\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.
